### 2017-04-04 paper/evaluation.tex
adjusting rq5
pass on eval

%% Regression tests that are well distributed may benefit from
%% parallelism since more tests executes at the same time while the
%% opposite scenario may require a different approach. In the later
%% scenario, executing tests in parallel may have insignificant impact
%% since a small subset of test cases dominates the execution.}

@@

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}), and compared their time cost with sequential
execution. We are interested in measuring the execution speedup (if
any) when the parallelization settings are activated.

>>>>

%% \Jbc{I shouldn't introduce parallelization arguments here but we have
%% to address this at some point:
%% Regression tests that are well distributed may benefit from
%% parallelism since more tests executes at the same time while the
%% opposite scenario may require a different approach. In the later
%% scenario, executing tests in parallel may have insignificant impact
%% since a small subset of test cases dominates the execution.}

@@

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default, and
compared their time cost with sequential execution. We are interested
in measuring the execution speedup (if any) when the parallelization
settings are activated.
